A Way Forward in Parallelising Dynamic Languages

### 2014-06-16 talk/icooolps2014/position-paper.tex
fix some references

\title{A Way Forward in Parallelising Dynamic Languages}
\subtitle{Position Paper, ICOOOLPS'14}

\authorinfo{Remigius Meier}
           {Department of Computer Science\\ ETH Zürich}
           {remi.meier@inf.ethz.ch}
\authorinfo{Armin Rigo}
           {www.pypy.org}
           {arigo@tunes.org}

@@

\bibitem{warmhoff13}
  Wamhoff, Jons-Tobias, et al. "FastLane: improving performance of
  software transactional memory for low thread counts."
  \emph{Proceedings of the 18th ACM SIGPLAN symposium on Principles
    and practice of parallel programming.} ACM, 2013.

\bibitem{drago11}
  Dragojević, Aleksandar, et al. "Why STM can be more than a research
  toy." \emph{Communications of the ACM} 54.4 (2011): 70-77.

\bibitem{cascaval08}
  Cascaval, Calin, et al. "Software transactional memory: Why is it
  only a research toy?." \emph{Queue} 6.5 (2008): 40.

@@

\bibitem{felber07}
  Felber, Pascal, et al. "Transactifying applications using an open
  compiler framework." \emph{TRANSACT}, August (2007): 4-6.

@@

\bibitem{spear09}
  Spear, Michael F., et al. "Transactional mutex locks." \emph{SIGPLAN
    Workshop on Transactional Computing.} 2009.

>>>>

\title{A Way Forward in Parallelising Dynamic Languages}
%\subtitle{Position Paper, ICOOOLPS'14}

\authorinfo{Remigius Meier}
           {Department of Computer Science\\ ETH Zürich, Switzerland}
           {remi.meier@inf.ethz.ch}
\authorinfo{Armin Rigo}
           {www.pypy.org}
           {arigo@tunes.org}

@@

\bibitem{warmhoff13}
  Jons-Tobias Wamhoff, Christof Fetzer, Pascal Felber, Etienne Rivière,
  and Gilles Muller. 2013. FastLane: improving performance of software
  transactional memory for low thread counts. \emph{SIGPLAN Not.} 48, 8
  (February 2013), 113-122.

\bibitem{drago11} Aleksandar Dragojević, Pascal Felber, Vincent
  Gramoli, and Rachid Guerraoui. 2011. Why STM can be more than a
  research toy. \emph{Commun. ACM} 54, 4 (April 2011), 70-77.

\bibitem{cascaval08}
  Calin Cascaval, Colin Blundell, Maged Michael, Harold W. Cain, Peng
  Wu, Stefanie Chiras, and Siddhartha Chatterjee. 2008. Software
  transactional memory: why is it only a research
  toy?. \emph{Commun. ACM} 51, 11 (November 2008), 40-46.

@@

\bibitem{felber07}
  Pascal Felber and Torvald Riegel and Christof Fetzer and Martin
  Süßkraut and Ulrich Müller and Heiko Sturzrehm. 2007. Transactifying
  applications using an open compiler framework. \emph{TRANSACT}, August
  (2007): 4-6.

@@

\bibitem{spear09}
  Luke Dalessandro, Dave Dice, Michael Scott, Nir Shavit, and Michael
  Spear. 2010. Transactional mutex locks. In \emph{Proceedings of the
    16th international Euro-Par conference on Parallel processing: Part
    II} (Euro-Par'10), Pasqua D'Ambra, Mario Guarracino, and Domenico
  Talia (Eds.). Springer-Verlag, Berlin, Heidelberg, 2-13.
